Naive Bayes Classifier

### 2019-02-25 NB_2r2c.Rmd
update

#Overview
This is the current version of the Naive Bayes workflow used to classify TA comments based on Subject and Structure. Features of **Version 2r.2c**:

@@

```{r writeCSV}
#Creates a data frame that compares predicted and actual labels for subject and structure
tallymatrix <- data.frame("text"=c(comments_rawVERB_R[1:9340,]$text),"subject_label"=c(comments_all_labels_subject), "subject_predicted"=c(comments_all_pred_subject),"structure_label"=c(comments_all_labels_structure), "structure_predicted"=c(comments_all_pred_structure))

@@

```{r}
ggplot(data=proptallysum1, aes(`Hand.Coded.Subject`, `total`,group=1))+
  geom_line()
ggplot(data=proptallysum2, aes(x=Bayes.Predicted.Subject, y=total, group=1))+
  geom_line()
ggplot(data=proptallysum3, aes(x=Hand.Coded.Structure, y=total, group=1))+
  geom_line()
ggplot(data=proptallysum4, aes(x=Bayes.Predicted.Structure, y=total, group=1))+
  geom_line()
```

>>>>

This is the current version of the Naive Bayes workflow used to classify TA comments based on Subject and Structure. Features of **Version 2r.2c**:

@@

```{writeCSV}
#Creates a data frame that compares predicted and actual labels for subject and structure
tallymatrix <- data.frame("text"=c(comments_rawVERB_R[1:9340,]$text),"subject_label"=c(comments_all_labels_subject), "subject_predicted"=c(comments_all_pred_subject),"structure_label"=c(comments_all_labels_structure), "structure_predicted"=c(comments_all_pred_structure))

@@

```{}
ggplot(data=proptallysum1, aes(`Hand.Coded.Subject`, `total`,group=1))+
  geom_line()
ggplot(data=proptallysum2, aes(x=Bayes.Predicted.Subject, y=total, group=1))+
  geom_line()
ggplot(data=proptallysum3, aes(x=Hand.Coded.Structure, y=total, group=1))+
  geom_line()
ggplot(data=proptallysum4, aes(x=Bayes.Predicted.Structure, y=total, group=1))+
  geom_line()
```
